---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# BrandsEyeR

[BrandsEye][brandseye] is a company that provides online monitoring, analytics,
and insights for social media data. We provide an extensive JSON / RESTful API
to access to the data that makes up your various BrandsEye accounts. This 
library is a wrapper for that API, and makes it easy to access the data outside
of the BrandsEye application in any [R][R] analyses that you might want to
perform.

## Installing

Installation is currently done via the [devtools package][devtools]:

```{r eval=FALSE}
# Install the devtools package
install.packages("devtools")
library(devtools)

# Install the library
install_github("brandseye/brandseyer")

# Load the library
library(brandseyer)
```

## Examples of use

You can create an account object using:

```{r eval=FALSE}
library(brandseyer)
ac <- account("QUIR01BA", key = "<MY API KEY>")    
```    

```{r include=FALSE}
library(brandseyer)
library(dplyr)
ac <- account("QUIR01BA")    # This requires you to be authenticated
```

and then you can query it using *account_count*:

```{r}
library(dplyr)
# Break down mention counts per country for the month of January, 2015.
filter <- "published after '2015/01/01' and published before '2015/02/01'"
countries <- account_count(ac, filter, groupby = "country") %>%
             # And here we sort by the count field using the dplyr package
             arrange(desc(count))
```

And here are the first few entries of the returned data frame:

```{r echo=FALSE}
knitr::kable(head(countries))
```
    
The call to BrandsEye can be simplified to one line, and can also be done 
across all of the accounts that you have:

```{r eval=FALSE}

account_count(list_account_codes(), 
              "published after '2015/01/01' and published before '2015/02/01'",
              groupby = "country")
```
    
## Authentication

You can automate this using the authenticate function:

    ?authenticate
    
Specifically, if you're happy having your credentials saved on your hard drive, 
you can do this:

```{r eval=FALSE}
authenticate(key = "<MY API KEY>", save = TRUE)
```
    
Please see the documentation for *authenticate* for some advice on securing that file.

Contact your client service representative to get your API key. If you are ever 
concerned that others may have acquired your key, contact client service and they'll
supply you with a new one (and invalidate your old).
    
## Documentation

All functions are documented within *R* itself. Interesting functions to read
up on are: 

* *account*
* *account_count*
* *list_account_codes*
    
The ultimate documentation for the filter language (the *filter* argument 
taken by many of the functions for selecting data sets) and the various
grouping and inclusions options is the [BrandsEye api documentation][api-docs]. 

## License

Copyright (c) 2015, Brandseye PTY (LTD) 

Permission is hereby granted, free of charge, to any person obtaining
a copy of this software and associated documentation files (the
"Software"), to deal in the Software without restriction, including
without limitation the rights to use, copy, modify, merge, publish,
distribute, sublicense, and/or sell copies of the Software, and to
permit persons to whom the Software is furnished to do so, subject to
the following conditions:

The above copyright notice and this permission notice shall be
included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE
LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION
OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION
WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

[R]: http://www.r-project.org/
[brandseye]: http://www.brandseye.com
[api-docs]: https://api.brandseye.com/docs
[devtools]: http://www.rstudio.com/products/rpackages/devtools/